Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-08 paper.tex
discussion os

\subsection{Discussion}
Again, the networking issue is restricting the performance of our executions, but it has been discussed during virtually all the paper.
However, it is not a new topic and in~\cite{tonithesis} is explained that investing in the network infrastructure could make the difference.

>>>>

\subsection{Discussion}
Again, the networking issue is restricting the performance of our executions, but it has been discussed during virtually all the paper.
However, it is not a new topic and in~\cite{tonithesis} is explained that improving the network infrastructure could make the difference.

The most remarkable achievement is the wide range of possible configuration and the freedom that would have an administrator to set and reset a system to fit the 
user requirements.

With an small investment in infrastructure and in maintenance can be fulfilled the requests of GPU-capable hosts in a completely transparent way for the user.
Energy can be saved, not only Thanks to the remote access and the ability to emulate several GPUs from a real one, but also  by grouping the accelerators in a single machine (when possible) or turning down nodes when their GPUs are not necessary.
